Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-02-04 submission5/core.tex
Intro nit

Of the mechanisms listed above, many are fundamentally ill suited for
offering formal guarantees: may impede attackers, but do not provide
universal protection. Shadow stacks, for instance, aim to ``restrict
the flexibility available in creating gadget chains''
\cite{Shanbhogue+19}, not to categorically rule out attacks. Other
mechanisms, such as Softbound\cite{NagarakatteZMZ09} and Code-pointer
integrity\cite{Kuznetsov+14}, do aim for stronger guarantees, but even
these do not make formal promises.  Indeed, to our knowledge, the sole
line of work making a formal claim to protect stack safety is the
secure calling conventions of Skorstengaard et
al.~\cite{SkorstengaardSTKJFP} and Georges et
al.~\cite{Georges22:TempsDesCerises}.

>>>>

Of the mechanisms listed above, many are fundamentally ill suited for
offering formal guarantees: may impede attackers, but do not provide
universal protection. Shadow stacks, for instance, aim to ``restrict
the flexibility available in creating gadget chains''
\cite{Shanbhogue+19}, not to categorically rule out attacks. Other
mechanisms, such as SoftBound~\cite{NagarakatteZMZ09} and code-pointer
integrity~\cite{Kuznetsov+14}, do aim for stronger guarantees, but even
these do not make formal promises.  Indeed, to our knowledge, the sole
line of work making a formal claim to protect stack safety is the
secure calling conventions of Skorstengaard et
al.~\cite{SkorstengaardSTKJFP} and Georges et
al.~\cite{Georges22:TempsDesCerises}.
